### 2019-10-31 letter.tex
substantial changes to letter

We have spent the last four months 
preparing a revised version of this paper. We thank the reviewers and meta-reviewer for their detailed,

@@

We have taken the feedback very seriously in preparing
the revised version, and we believe the paper is substantially
stronger as a result. \newsaj{The revision necessitated a number of updates to the content of each section and are highlighted in teal color. In Section 1, we cited existing work that highlight the widespread adoption of spreadsheets even among users of advanced enterprise solutions, adding further merit to our goal of addressing navigation challenges within spreadsheets. Recent discourse within the visualization community also echoes our sentiment\footnote{https://twitter.com/FILWD/status/1187411664611749888}---instead of designing a new tool that may cater to a small population, we aim to improve user experience with spreadsheet tools boasting more than $700$ million users. Moreover, we augmented the definitions of spreadsheet interactions like scrolling and steering and clearly articulated the challenges of designing a general purpose plug-in for spreadsheets. In Section 2, we defined the scope of tasks supported by spreadsheets guided by existing taxonomy of abstract visualization tasks. We further enhanced our usage scenario by highlighting how different use cases of \noah maps to the scope defined for spreadsheets. In Section 5, we added additional discussions to clearly articulate the difference in the goals of spreadsheets spreadsheets and TDA tools which further justifies choice of Excel, the most widely used spreadsheet tool, as our baseline in the evaluation study. In Section 4, we added further clarification to the third design consideration (\textbf{DC3}). In Section 5, we provided justifications for developing a multi-granularity overview while explaining why we opted for histogram as an overview representation. In Section 6, we further clarified the goals of the evaluation study while rephrasing the research questions to better reflect those goals. We didn't alter our previous research questions, rather grouped a few research questions into a more high level and less ambiguous question. Moreover, we explained our choice of the quiz tasks and discussed three limitations of our study in detail. We revamped Section 7 completely to better reflect our research questions while adding more qualitative observations regarding the user experience with \noah. We also included an additional analysis on the intra-participant differences. In Section 8, we first added a summary of our takeaways from the evaluation study while discussing additional limitations of \noah and future enhancement opportunities. We now discuss how the updates made to all of these sections addressed the changes suggested by the reviewers.}

@@

\item \textit{Merits over other tools} (\textbf{C1}): \saj{In the paper, we have identified the major contribution of \noah as its \emph{design as a general purpose navigation plug-in} to any existing spreadsheet. As spreadsheets have a massive user-base, enhancing exploration and formula computation on large datasets while maintaining the spreadsheet look and feel as much as possible, has the potential to impact a lot of users. Most of these users employ spreadsheets as their primary data management and analysis tool while shunning enterprise solutions with more advanced features. Therefore, our goal is to develop a solution to improve navigation within spreadsheets.}

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): We have explained our choice of the binning mechanism in the context of the third design consideration (\emph{DC3}). This explanation can be found under the title ``Why a Multi-granularity Binned Overview'' in Section~\ref{sec:design}. \saj{In brief, we opted for binning to provide a clear and concise representation of the overall data distribution while minimizing user's back and forth movement across multiple screens during navigation.} However, we acknowledge limitation of this choice for binning categorical data and discuss possible solutions in Section~\ref{sec:discuss} in the context of our user study findings.

\item \textit{Justification of Excel as a Baseline} (\textbf{C2}):
We have provided justification for using Excel over tabular data analysis (TDA) tools a) by highlighting the appeal of spreadsheets among users who shun more advanced enterprise solutions (see Section~\ref{sec:intro}), b) by identifying the scope of tasks supported by spreadsheets and TDA tools (see Section~\ref{sec:usage} and~\ref{sec:related}), c) by explaining that the goal of spreadsheets is to present the raw data as is, amenable to editing, formula computation, and comparison of derived data unlike TDA tools that hide the data while providing summarized statistics (see Section~\ref{sec:related}), and d) by highlighting the importance of addressing the shortcomings of a tool, the user base of which far exceeds that of TDA tools (see Section~\ref{sec:study_design}).

\item \textit{Enhancing the user study design} (\textbf{C4, C5}):
We have added additional explanations regarding the goal of the study while better articulating the research questions, provided a better justification for the choice of the tasks for the study (see Section~\ref{sec:study_design}) and added a detailed discussion on the limitations of the study. \saj{Specifically, we merged a number of research questions that explored how specific features of \noah affected participants' navigation experience into one broad question which explores their overall experience with \noah and its components. Moreover, we have justified the choice of the quiz tasks by a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}), and b) explaining how these tasks can reveal how people may use \noah for spreadsheet navigation. Finally, we have identified two limitations of the study, resulting from the sample size and the study design, which we justify based on the scope of the study.}

\item \textit{Reporting Intra-participant Differences} (\textbf{C6}):
Finally, we have performed additional analysis of the study data to report intra-participant submission time differences while providing insights on the trends that emerged from analyzing the data. \saj{For the latter, we find that, despite a few exceptions, across all tasks, participants' task submission times were faster using \noah. However, we already obtained similar observations from Figure~\ref{fig:timeBox} in Section~\ref{sec:rq1}. Therefore, we have included the results of the intra-participant analysis in appendix while briefly summarizing its outcomes in Section~\ref{sec:rq1}.}
\end{enumerate}

>>>>

\new{We thank the reviewers and meta-reviewer for their detailed,

@@

Taking this feedback into account, 
we have spent the last four months 
preparing a revised version of this paper.
We believe the paper is substantially
stronger as a result. 
Every section in the paper has been revised;
the changes are highlighted in blue.
We briefly describe the changes to each section
before returning to the changes required in the revision 
({\bf C1}--{\bf C6}).
\subsection*{Changes Organized by Section}
	\leftmargin=25pt \rightmargin=0pt \labelsep=5pt \labelwidth=20pt \itemindent=0pt \listparindent=0pt \topsep=0pt plus 2pt minus 4pt \partopsep=0pt plus 1pt minus 1pt \parsep=0pt plus 1pt \itemsep=\parsep
\item 
In Section~\ref{sec:intro}, we now cite
work that highlights the widespread adoption
of spreadsheets even among users of 
advanced enterprise solutions, further justifying 
why we focused on addressing navigation challenges within
spreadsheets. In fact, recent 
debate within the visualization community following
VIS 2019 also echoes this view\footnote{https://twitter.com/FILWD/status/1187411664611749888}---instead of designing a new sophisticated tool from scratch that 
may cater to a small population, 
we aim to enhance the user experience for
existing spreadsheet tools
with nearly a billion users.
Furthermore, in Section~\ref{sec:intro},  
the definitions of spreadsheet 
interactions like scrolling and steering have been augmented, and 
we now clearly articulate the challenges of 
designing a general-purpose plug-in for spreadsheets.
\item 
In Section~\ref{sec:usage}, 
our usage scenario has been substantially revised 
using Brehmer and Munzner's typology~\cite{brehmer2013multi} to
clarify the scope of tasks supported by 
a \noah-enhanced spreadsheet; our new Table~\ref{tab:scope}
provides use-cases supported within \noah
for each category.
\item
In Section~\ref{sec:related},
we now clearly
articulate the differences in goals
of spreadsheets and tabular data analysis tools (TDA),
further justifying our choice of Excel,
the most widely used spreadsheet tool,
as our baseline in the evaluation study.
\item 
In Section~\ref{sec:design},
we now explain the  
third design consideration 
for \noah more clearly
(\textbf{DC3})---focusing on motivating the binning
mechanism. 
\item In Section~\ref{sec:ui}, 
we now justify why we are developing a 
multi-granularity overview,
and explain why 
we opted for histograms as an overview representation. 
\item 
In Section~\ref{sec:study}, 
we further clarified the goals of our study
and reframed our research questions to 
better reflect those goals. 
Our research questions haven't been substantially altered;
rather, they have been grouped together and made less
ambiguous. In this version,
we now explain our choice
for the quiz tasks and discuss 
three limitations of our study in detail. 
\item Section~\ref{sec:results} has been completely
revamped to better reflect our research questions,
while adding more qualitative observations 
regarding the user experience with \noah. 
We now
include additional analysis results on intra-participant differences. 
\item In Section~\ref{sec:discuss}, we have added a summary of our takeaways from the evaluation study, while discussing additional limitations of \noah and future enhancement opportunities. 
\subsection*{Changes Organized by Reviewer Concerns (C1--C6)}
}

@@

\item \textit{Merits over other tools} (\textbf{C1}): 
\new{Throughout the paper (and especially in 
Sections~\ref{sec:intro}, \ref{sec:related},
and \ref{sec:study}), we have emphasized
that the main contribution of \noah
is its \emph{design as a general-purpose navigation plug-in} 
to any existing spreadsheet system. 
As spreadsheets have a massive user-base, 
enhancing exploration and formula computation 
on large datasets while maintaining 
the spreadsheet look-and-feel as much as possible, 
has the potential to impact hundreds of millions 
of spreadsheet users. 
Most of these users employ spreadsheets 
as their primary data management and analysis 
tool while shunning enterprise solutions 
with more advanced features. 
Therefore, our goal is to develop a 
solution to improve navigation within spreadsheets.
Indeed, we could have tried to enhance navigation
in other tools, such as Keshif, or Tableau, like
the reviewers suggest---but we would be forcing
spreadsheet users to adopt an entirely new tool, something
that they are clearly loath to do.}

\item \textit{Explanation of the binning mechanism} (\textbf{C2}): 
\new{We now explain our choice
of the binning mechanism in 
the context of the third design consideration (\emph{DC3}), 
as detailed in Section~\ref{sec:design}.
We further expand on this in the blurb titled 
``Why a Multi-granularity Binned Overview'' 
in Section~\ref{sec:ui}.
In brief, we opted for binning to 
provide a clear and concise 
representation of the overall data 
distribution while minimizing user's back 
and forth movement across multiple screens 
during navigation. 
At some level, we do need to limit the number
of values displayed so that the overview
fits on the screen: binning is a natural solution
for that issue. 
\agp{Possibly argue using the immens paper?}
However, we acknowledge limitations 
for this choice for binning categorical data 
and discuss possible solutions 
in Section~\ref{sec:discuss} 
in the context of our user study findings. 
}

\item \textit{Justification of Excel as a Baseline} (\textbf{C2}):
\new{Since our goal is to improve spreadsheet
user experience---and there are very good reasons for doing so,
as outlined in item 1) above---the natural comparison point
is Excel. 
That said, beyond popularity, 
we have provided a thorough justification
for what spreadsheet systems like Excel offer
relative to tabular data analysis tools (TDA),
making it a more appropriate point of comparison.
Our justification for using Excel over 
tabular data analysis (TDA) tools involves 
a) highlighting the appeal of spreadsheets 
among users who shun more advanced enterprise 
tools (Section~\ref{sec:intro}), 
b) identifying the scope of tasks 
supported by spreadsheets and 
TDA tools (Section~\ref{sec:usage} and~\ref{sec:related}), 
c) explaining that the goal of spreadsheets 
is to present the raw data as is, 
amenable to editing, formula computation, and comparison of derived data, all done in-situ,
unlike TDA tools that hide the data 
while providing summarized statistics 
(Section~\ref{sec:related}), and 
d) highlighting the importance of 
addressing the shortcomings of a tool, 
the user base of which far exceeds 
that of TDA tools (Section~\ref{sec:study}). 
}

\item \textit{Enhancing the user study design} 
(\textbf{C4, C5}):
\agp{Revise to clarify where these changes are made
and HOW these changes solve the issue. Just saying
we merged doesn't necessarily address the issue.}
We have added additional 
explanations regarding the goal 
of the study while better articulating 
the research questions, provided a better justification for the choice of the tasks for the study (see Section~\ref{sec:study_design}) and added a detailed discussion on the limitations of the study. \saj{Specifically, we merged a number of research questions that explored how specific features of \noah affected participants' navigation experience into one broad question which explores their overall experience with \noah and its components. Moreover, we have justified the choice of the quiz tasks by a) relating their goals with the scope of tasks supported by spreadsheets (see Section~\ref{sec:usage}), and b) explaining how these tasks can reveal how people may use \noah for spreadsheet navigation. Finally, we have identified two limitations of the study, resulting from the sample size and the study design, which we justify based on the scope of the study.}

\item \textit{Reporting Intra-participant Differences} (\textbf{C6}):
\new{We performed additional analysis of the study data to report intra-participant submission time differences while providing insights on the trends that emerged from analyzing the data: this new analysis can be found in XXX\agp{pls add; insights on trends sounds vague let's be more clear}.} \saj{For the latter, we find that, despite a few exceptions, across all tasks, participants' task submission times were faster using \noah. However, we already obtained similar observations from Figure~\ref{fig:timeBox} in Section~\ref{sec:rq1}. Therefore, we have included the results of the intra-participant analysis in appendix while briefly summarizing its outcomes in Section~\ref{sec:rq1}.}
\end{enumerate}
